\thispagestyle{empty}

%TC:ignore

\section*{\centering Abstract}

Web and Mobile Technologies have become increasingly ubiquitous in the travel and tourism industry. These technologies, together with a company's ability to successfully adopt them is often pivotal to the company's success within the industry.

This project's aim was to provide a platform for local taxi companies to interact with and provide a service for their customers. The key aspect of the platform is the creation, viewing, and management of bookings. By handling bookings this way, customers and taxi companies can reliably keep track of their past and present bookings in real time.

This project has produced a fit for purpose, fully functional platform. It is split into 3 key systems: a REST API to interact with the backend database and be consumed by other systems within the platform; a web app to be used by controllers within a company to claim, delegate, and manage bookings; and an Android App to be used by customers and drivers to view, create, and manage bookings. The developed product is flexible, allowing taxi companies to choose the level of adaptation that would best fit their business.

Predictably, however, there is room for improvement and future development within the project. Given the scope and time restrictions provided, the produced platform is only intended as a starting point and proof of concept.

This document will provide an insight into the motivation behind platform's development, address weaknesses and key areas for improvement, and discuss the engineering and project management challenges encountered and how they were overcome.

%TC:endignore